---
title: "Study 6a & 6b"
output: html_document
---
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(lmerTest)
library(car)
library(lme4)
library(BayesFactor)
library(gridExtra)
library(cowplot)
library(optimx)
```

#Load data
```{r}
#Study 6a for "man"
dm = read.csv("~/Desktop/Stanford/Dual Character Concepts/Dual Character Concept Data/Study 6a Man.csv")

#Study 6a for "woman"
dw = read.csv("~/Desktop/Stanford/Dual Character Concepts/Dual Character Concept Data/Study 6a Woman.csv")

#Study 6b for "man"
dms = read.csv("~/Desktop/Stanford/Dual Character Concepts/Dual Character Concept Data/Study 6b Man.csv")

#Study 6b for "woman"
dws = read.csv("~/Desktop/Stanford/Dual Character Concepts/Dual Character Concept Data/Study 6b Woman.csv")
```

#set function for getting 95% bootstrapped confidence intervals
```{r}
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - mean(x,na.rm=na.rm)}
```

#Demographics of 6a
```{r}
dw_1 = dw %>% # selecting Gender and Age variables for the "woman" dataset in 6a
  dplyr::select(Gender, Age)

dm_1 = dm %>% # selecting Gender and Age variables for the "man" dataset in 6a
  dplyr::select(Gender, Age)

d_demo_6a = rbind(dw_1, dm_1) #combining the two versions

summary(d_demo_6a$Age) #participant age info
summary(as.factor(d_demo_6a$Gender)) #participant ender info
```
#Demographics of 6b
```{r}
#Demographics
dws_1 = dws %>% # selecting Gender and Age variables for the "woman" dataset in 6b
  dplyr::select(Gender, Age)
dms_1 = dms %>% # selecting Gender and Age variables for the "man" dataset in 6b
  dplyr::select(Gender, Age)

d_demo_6b = rbind(dws_1, dms_1) #combining the two versions

summary(d_demo_6b$Age) # participant age info
summary(as.factor(d_demo_6b$Gender)) # participant gender info
```

#Experiment 6a specificity of statements for "man"
```{r}
#turn data into long form
d6am = dm %>%
  mutate(index=104:204) %>% #numbering participants starting from 104 for later combining with the "woman" dataset
  gather(Concept, value, Cowardly:Not.Taking.Action.When.Significant.Others.Threatened) %>%
  group_by(index)

#labeling items according to whether they describe more general or more specific gendered traits and the non-gendered neutral ones
d6am = within(d6am, {Type = ifelse(Concept %in% c("Cowardly", "Emotional", "Abusive", "Dishonest", "Sensitive", "Irresponsible", "Submissive", "Narcissistic", "Bragging", "Dishonorable", "Disrespectful", "Gossipy", "Weak"), "General", ifelse(Concept %in% c("Easygoing", "Traveling", "Swimming", "Smiling", "Music", "Reading", "Movie", "Environment", "Curious", "Kind"), "Neutral", "Concrete"))})

d6am$Type = as.factor(d6am$Type)

#compare the 3 kinds of statements
lm_6am = lmer(value~relevel(Type, ref = "General")+(0+Type||index)+(1|Concept), d6am) #the maximal model didn't converge -- we therefore modified the model following the advice by Bates et al. (2015).
summary(lm_6am)
anova(lm_6am)

#change reference level
lm_6am_relevel = lmer(value~relevel(Type, ref = "Concrete")+(0+Type||index)+(1|Concept), d6am) #the maximal model didn't converge -- we therefore modified the model following the advice by Bates et al. (2015).
summary(lm_6am_relevel)
anova(lm_6am_relevel)

rank_graph_6am = d6am %>%
  group_by(Concept, Type) %>%
  summarise(Mean = mean(value, na.rm=T))

ggplot(rank_graph_6am, aes(x=reorder(Concept, Mean), y=Mean, fill = Type, label = round(Mean, digits=2))) + geom_bar(width = .5, stat="identity",position = position_dodge(width = .5)) + ggtitle("Rank Order of Degree of Violation of Man by Concept") + scale_x_discrete(name = "Concept") + scale_fill_manual(values = c("grey85", "skyblue2", "beige")) +  scale_y_continuous(name="Mean Ratings for Violation", breaks = c(1:7), sec.axis = sec_axis(~.*1, name = "Mean Rating for Violation", breaks = c(1:7)))+ coord_flip(ylim=c(1,7)) + theme (axis.text.x = element_text(vjust=0.7, size=8, angle=0)) + theme (axis.text.y = element_text(vjust=0.7, size=6, angle=0))
```

#Experiment 6a comparing stereotypic vs. moral items for "man"
```{r}
#selecting moral and stereotypic items
dmn = d6am %>%
  filter(Concept %in% c("Cowardly", "Emotional", "Submissive", "Gossipy", "Crying", "Caring.about.Appearance", "Not.Sticking.Up.for.Himself", "Dishonorable", "Abuse.Children", "Abuse.Spouse", "Cheating.on.Spouse", "Not.Taking.Action.When.Significant.Others.Threatened", "Not.Taking.Responsibilities", "Gambling.Away.Savings", "Not.Standing.Up.for.What.He.Believes.In", "Disrespectful"))

#sorting the items into "stereotypical" or "moral"
dmn = within(dmn, {Type = ifelse(Concept %in% c("Cowardly", "Emotional", "Submissive", "Gossipy", "Crying", "Caring.about.Appearance", "Not.Sticking.Up.for.Himself", "Not.Standing.Up.for.What.He.Believes.In"), "Stereotypical", "Moral")})

#check the items
unique(dmn$Concept)

##compare stereotypic vs. moral in ideal image violation:
ln1 = lmer(value~Type+(1+Type|index)+(1|Concept), dmn)
summary(ln1)
anova(ln1)

#rank order bar graph for moral and stereotypic items in how serious violations participants perceived them to be of their ideal images of "man""
aggmn = dmn %>%
  group_by(Concept, Type) %>%
  summarise(Mean = mean(value, na.rm=T),
            upper = Mean+ci.high(value),
            lower = Mean-ci.low(value))

ggplot(aggmn, aes(x=reorder(Concept, Mean), y=Mean, fill = Type, label = round(Mean, digits=2))) + geom_bar(width = .5, stat="identity",position = position_dodge(width = .5)) + scale_x_discrete(name = "Transgression Item") + scale_fill_manual(values = c("grey85", "skyblue2")) + scale_y_continuous(name="How serious a violation of the ideal image of a man", breaks = c(1:7), sec.axis = sec_axis(~.*1, name = "How serious a violation of the ideal image of a man", breaks = c(1:7)))+ coord_flip(ylim=c(1,7)) + theme (axis.text.x = element_text(vjust=0.7, size=8, angle=0)) + theme (axis.text.y = element_text(vjust=0.7, size=9, angle=0))+theme_bw()+geom_bar(position="dodge", stat="identity", col = "black")+geom_errorbar(   aes( ymax=upper, ymin=lower ) , 
                     		width   =.25,
	                    	linetype="solid", position=position_dodge(.9)
	                    	)

#test whether the aggregate scores were signiticantly different from the mid-point (4) on the scale.
t.test(subset(dmn, Type == "Moral")$value, mu=4)
t.test(subset(dmn, Type == "Stereotypical")$value, mu=4)
```

#Experiment 6a specificity of statements for "woman"
```{r}
#turn data into long form
d6aw = dw %>%
  mutate(index=1:103) %>%
  gather(Concept, value, Dominant:Not.Taking.Action.When.Significant.Others.Threatened) %>%
  group_by(index)

#sort data into categories
d6aw = within(d6aw, {Type = ifelse(Concept %in% c("Dominant", "Emotionally Cold", "Abusive", "Dishonest", "Promiscuous", "Messy", "Aggressive", "Calculating", "Rude", "Vulgar", "Disrespectful", "Intimidating", "Impatient"), "General", ifelse(Concept %in% c("Easygoing", "Traveling", "Swimming", "Smiling", "Music", "Reading", "Movie", "Environment", "Curious", "Kind"), "Neutral", "Concrete"))})

#factorize the variable
d6aw$Type = as.factor(d6aw$Type)

#compare the 3 kinds of statements
lm_6aw = lmer(value~Type+(0+Type||index)+(1|Concept), d6aw)
summary(lm_6aw)
anova(lm_6aw)

#change reference level
lm_6aw_relevel = lmer(value~relevel(Type, ref = "General")+(0+Type||index)+(1|Concept), d6aw)
summary(lm_6aw_relevel)
anova(lm_6aw_relevel)

#get stats for creating the graph
rank_order_6aw = d6aw %>%
  group_by(Concept, Type) %>%
  summarise(Mean = mean(value, na.rm=T))

#graph for 6a woman
ggplot(rank_order_6aw, aes(x=reorder(Concept, Mean), y=Mean, fill = Type, label = round(Mean, digits=2))) + geom_bar(width = .5, stat="identity",position = position_dodge(width = .5)) + ggtitle("Rank Order of Degree of Violation of Woman by Concept") + scale_x_discrete(name = "Concept") + scale_fill_manual(values = c("grey85", "skyblue2", "beige")) +  scale_y_continuous(name="Mean Ratings for Violation", breaks = c(1:7), sec.axis = sec_axis(~.*1, name = "Mean Rating for Violation", breaks = c(1:7)))+ coord_flip(ylim=c(1,7)) + theme (axis.text.x = element_text(vjust=0.7, size=8, angle=0)) + theme (axis.text.y = element_text(vjust=0.7, size=6, angle=0))
```

#Experiment 6a comparing stereotypic vs. moral items for "woman"
```{r}
#select moral and stereotypical items
dwn = d6aw %>%
  filter(Concept %in% c("Dominant", "Wanting.To.Be.Boss", "Rude", "Vulgar", "Not.Wanting.Children", "Emotionally.Cold", "Not.Cleaning.House", "Not.Caring.about.Appearance", "Promiscuous", "Abuse.Spouse", "Abuse.Children", "Cheating.on.Spouse", "Initiating.Fights", "Disrespectful", "Not.Taking.Action.When.Significant.Others.Threatened", "Spendthrift.on.Cosmetics.and.Clothing"))

#sort items into either "stereotypical" or "moral"
dwn = within(dwn, {Type = ifelse(Concept %in% c("Dominant", "Wanting.To.Be.Boss", "Rude", "Vulgar", "Not.Wanting.Children", "Emotionally.Cold", "Not.Cleaning.House", "Not.Caring.about.Appearance"), "Stereotypical", "Moral")})

#compare moral vs. stereotypical for "woman"
ln2 = lmer(value~Type+(1+Type|index)+(1|Concept), dwn)
summary(ln2)

#get stats for the graph
aggwn = dwn %>%
  group_by(Concept, Type) %>%
  summarise(Mean = mean(value, na.rm=T),
            upper = Mean + ci.high(value),
            lower = Mean - ci.low(value))

#create the graph
ggplot(aggwn, aes(x=reorder(Concept, Mean), y=Mean, fill = Type, label = round(Mean, digits=2))) + geom_bar(width = .5, stat="identity",position = position_dodge(width = .5)) + scale_x_discrete(name = "Transgression Item") + scale_fill_manual(values = c("grey85", "skyblue2")) + scale_y_continuous(name="How serious a violation of the ideal image of a woman", breaks = c(1:7), sec.axis = sec_axis(~.*1, name = "How serious a violation of the ideal image of a woman", breaks = c(1:7)))+ coord_flip(ylim=c(1,7)) + theme (axis.text.x = element_text(vjust=0.7, size=8, angle=0)) + theme (axis.text.y = element_text(vjust=0.7, size=9, angle=0))+theme_bw()+geom_bar(position="dodge", stat="identity", col = "black")+geom_errorbar(   aes( ymax=upper, ymin=lower ) , 
                     		width   =.25,
	                    	linetype="solid", position=position_dodge(.9)
	                    	)

#t-test comparing whether the aggregate ratings for moral vs. stereotypical items were significantly different from the mid-point (4) of the scale.

t.test(subset(dwn, Type == "Moral")$value, mu=4)
t.test(subset(dwn, Type == "Stereotypical")$value, mu=4)
```

#Experiment 6a comparing "man" and "woman"
```{r}

#add version name "woman" for the "man" vs. "woman" variable in the joint dataset 
dmn1 = dmn %>%
  mutate(version = "M")

#add version name "man" for the "man" vs. "woman" variable in the joint dataset 
dwn1 = dwn %>%
  mutate(version = "W")

#create the joint dataset
dnorm = rbind(dmn1, dwn1)
dnorm = na.omit(dnorm) %>%
  mutate(Type = as.factor(Type))

#compare man and woman
lnorm = lmer(value~Type*version+(1+Type|index)+(1|Concept), dnorm)
summary(lnorm)
anova(lnorm)

#get specific comparisons for how moral and stereotypic items, respectively, were rated differently for "man" and "woman"
lsmeansLT(lnorm)

#get stats for the graph
aggnorm = dnorm %>%
  group_by(Type, version) %>%
  summarize(value = mean(value, na.rm=T)
            )

#create the graph
ggplot(aggnorm, aes(x = Type, y = value, fill = version))+geom_bar(width = .5, stat="identity",position = position_dodge(width = .5)) +  scale_fill_manual(values = c("grey85", "skyblue2")) +theme_bw()

```

#Experiment 6b "man"
```{r}
#turn the data into long form
d6bm = dms %>%
  mutate(index=1:151) %>%
  gather(Concept, value, Cowardly:Caring.about.Appearance) %>%
  group_by(index)

#sort the items into "stereotypical" and "moral"
d6bm = within(d6bm, {Type = ifelse(Concept %in% c("Cowardly", "Emotional", "Submissive", "Gossipy", "Crying", "Caring.about.Appearance", "Not.Sticking.Up.for.Himself", "Not.Standing.Up.for.What.He.Believes.In"), "Stereotypical", "Moral")})

#get stats for making the bar graph
graph_6bm = d6bm %>%
  group_by(Concept, Type) %>%
  summarise(Mean = mean(value, na.rm=T),
            upper = Mean+ci.high(value),
            lower = Mean-ci.low(value))

#creating the graph
ggplot(graph_6bm, aes(x=reorder(Concept, Mean), y=Mean, fill = Type, label = round(Mean, digits=2))) + geom_bar(width = .5, stat="identity",position = position_dodge(width = .5)) + scale_x_discrete(name = "Transgression Item") + scale_fill_manual(values = c("grey85", "skyblue2")) + scale_y_continuous(name="Participants' endorsement of 'not truly a man'", breaks = c(1:7), sec.axis = sec_axis(~.*1, name = "Participants' endorsement of 'not truly a man'", breaks = c(1:7)))+ coord_flip(ylim=c(1,7)) + theme (axis.text.x = element_text(vjust=0.7, size=8, angle=0)) + theme (axis.text.y = element_text(vjust=0.7, size=9, angle=0))+theme_bw()+geom_bar(position="dodge", stat="identity", col = "black")+geom_errorbar(   aes( ymax=upper, ymin=lower ) , 
                     		width   =.25,
	                    	linetype="solid", position=position_dodge(.9)
	                    	)

##compare how well ratings for items in 6a correlate with ratings in the current survey [6b]
dmss = d6bm %>% #ratings in 6b
  group_by(Concept) %>%
  summarise(Means = mean(value, na.rm=T))

dmnn = dmn %>% #ratings from 6a
  group_by(Concept) %>%
  summarise(Meann = mean(value, na.rm=T))

#join the the two datasets
d_joint_m = merge(dmnn, dmss)

#test the correlation between ratings of the two experiments for the same items. 
cor.test(d_joint_m$Meann, d_joint_m$Means)

----------------------------------------------------

#test whether mean for moral is significantly greater than 4
t.test(subset(d6bm, Type == "Moral")$value, mu=4)

#test whether mean for stereotypical is significantly less than 4
t.test(subset(d6bm, Type == "Stereotypical")$value, mu=4)
```

#Experiment 6b "woman"
```{r}
#turn data into long form
d6bw = dws %>%
  mutate(index=152:303) %>%
  gather(Concept, value, Dominant:Not.Caring.about.Appearance) %>%
  group_by(index)

#sort items into "stereotypical" and "moral"
d6bw = within(dws_tidy, {Type = ifelse(Concept %in% c("Dominant", "Wanting.To.Be.Boss", "Rude", "Vulgar", "Not.Wanting.Children", "Emotionally.Cold", "Not.Cleaning.House", "Not.Caring.about.Appearance"), "Stereotypical", "Moral")})

#get stats for graph
aggws = dws_tidy %>%
  group_by(Concept, Type) %>%
  summarise(Mean = mean(value, na.rm=T),
            upper = Mean+ci.high(value),
            lower = Mean-ci.low(value))

#create graph
ggplot(aggws, aes(x=reorder(Concept, Mean), y=Mean, fill = Type, label = round(Mean, digits=2))) + geom_bar(width = .5, stat="identity",position = position_dodge(width = .5)) + scale_x_discrete(name = "Transgression Item") + scale_fill_manual(values = c("grey85", "skyblue2")) + scale_y_continuous(name="Participants' endorsement of 'not truly a woman'", breaks = c(1:7), sec.axis = sec_axis(~.*1, name = "Participants' endorsement of 'not truly a woman'", breaks = c(1:7)))+ coord_flip(ylim=c(1,7)) + theme (axis.text.x = element_text(vjust=0.7, size=8, angle=0)) + theme (axis.text.y = element_text(vjust=0.7, size=9, angle=0))+theme_bw()+geom_bar(position="dodge", stat="identity", col = "black")+geom_errorbar(   aes( ymax=upper, ymin=lower ) , 
                     		width   =.25,
	                    	linetype="solid", position=position_dodge(.9)
	                    	)

##compare how well ratings for items in 6a correlate with ratings in the current survey [6b]
dwss = d6bw %>%
  group_by(Concept) %>%
  summarise(Means = mean(value, na.rm=T))

dwnn = dwn %>%
  group_by(Concept) %>%
  summarise(Meann = mean(value, na.rm=T))

#join the two datasets
d_joint_w = merge(dwnn, dwss)

##test the correlation between ratings of the two experiments for the same items. 
cor.test(d_joint_w$Meann, d_joint_w$Means)

----------------------------------------------------
  
#test whether mean for moral is significantly less than 4 in 6b
t.test(subset(d6bw, Type == "Moral")$value, mu=4)

#test whether mean for stereotypical is significantly less than 4 in 6b
t.test(subset(d6bw, Type == "Stereotypical")$value, mu=4, alternative="less")
```

#Combine "man" and "woman" for 6b
```{r}
#select relevant variables
vark = c("value", "Type", "Concept", "index")
dws1 = d6bw[vark] #for "woman" in 6b

#add version name "woman" for the "man" vs. "woman" variable in the joint dataset 
dws1 = dws1 %>%
  mutate(version = "W")

#select relevant variables
dms1 = d6bm[vark] # for "man" in 6b

#add version name "man" for the "man" vs. "woman" variable in the joint dataset 
dms1 = dms1 %>%
  mutate(version = "M")

#create the joint dataset
d_joint_c = rbind(dws1, dms1)
```

#combine 6a and 6b for analysis
```{r}
#combining the datasets for 6a & 6b for "woman""
dws11 = merge(dws1, dwnn, by.x = "Concept")
#combining the datasets for 6a & 6b for "man""
dms11 = merge(dms1, dmnn, by.x = "Concept")
#join combined man and woman datasets
d_joint_p = rbind(dws11, dms11) %>%
  mutate(Type = as.factor(Type),
         version = as.factor(version))

rank_1w = dws1 %>%
    group_by(Concept) %>%
  summarise(Mean = mean(value, na.rm=T))

rank_1m = dms1 %>%
  group_by(Concept) %>%
  summarise(Mean = mean(value, na.rm=T))

#spearman rank order correlation to see whether the ranking of the items in 6a correlates with the ranking of the same items in 6b for "man" and "woman"
cor.test(rank_1w$Mean, dwnn$Meann, method = "spearman")
cor.test(rank_1m$Mean, dmnn$Meann, method = "spearman")

#compare the model that considers the Exp. 6a ratings as a covariate and the model that doesn't consider the ratings as a covariate.

pmix1 = lmer(value~Meann+Type*version+(1+Meann|Concept)+(1+Type|index), d_joint_p) #including the covariate
pmix2 = lmer(value~Type*version+(1|Concept)+(1+Type|index), d_joint_p) #excluding the covariate

anova(pmix1, pmix2)

#model 1 is significantly better

summary(pmix1)
anova(pmix1)

#planned contrasts for specific comparisons
difflsmeans(pmix1)
```
