---
title: "Study 3 Master File"
author: "Cai Guo"
date: "01/24/2018"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
---
#Study 3a
```{r message=FALSE, warning=FALSE, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(lmerTest)
library(car)
library(lme4)
library(BayesFactor)
library(gridExtra)
library(cowplot)
library(RePsychLing)
```

##Set functions
```{r}
#set function for getting standardized coefficients for lmer models
stdCoef.merMod <- function(object) {
  sdy <- sd(getME(object,"y"))
  sdx <- apply(getME(object,"X"), 2, sd)
  sc <- fixef(object)*sdx/sdy
  se.fixef <- coef(summary(object))[,"Std. Error"]
  se <- se.fixef*sdx/sdy
  return(data.frame(stdcoef=sc, stdse=se))
}

#set function for bootstrapping 95% CIs
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - mean(x,na.rm=na.rm)}
```

##Load Data
```{r message=FALSE, warning=FALSE, include=FALSE}
dv = read.csv("~/Desktop/Stanford/Dual Character Concepts/Dual Character Concept Data/Study 3a.csv")

#Remove participants who did not answer the attention check question correctly.
dv = dv %>%
  filter(Filter==1)

#Turn dataset into long form. 
dv_tidy = dv %>%
  mutate(index=rownames(dv)) %>%
  gather(variable, value, Clear.Art:Ultim.Woman) %>%
  group_by(index) %>%
  separate(variable, into=c("Statement", "Concept"))

#Label variables
dv_tidy$Statement = as.factor(dv_tidy$Statement)
levels(dv_tidy$Statement)[levels(dv_tidy$Statement)=="Clear"] <- "Member"
levels(dv_tidy$Statement)[levels(dv_tidy$Statement)=="Ultim"] <- "Nonmember"

dv_c = within(dv_tidy, {Type = ifelse(Concept %in% c("Art", "Criminal", "Love", "Friend", "Mentor", "Comedian", "Minister", "Theory", "Boyfriend", "Argument"), "DualCharacter", ifelse(Concept %in% c("Rustling", "Welder", "Catalog", "Chair", "Firefighter", "Uncle", "Cashier", "Stroller", "Obituary", "Cousin"), "Control", ifelse(Concept %in% c("Man", "Woman"), "Gender", "NaturalKind")))})

```

##Demographics
```{r message=FALSE, warning=FALSE}
#1 = Female, 2 = Male, 3 = Other
prop.table(table(dv$Gender))
#Age
summary(dv$Age)
```

##Compare Man and Woman to decide whether to combine or separate them in subsequent analyses.
```{r message=FALSE, warning=FALSE}
#since there's only 1 concept within Man and Woman respectively, we do not include Concept but only subject (index) as a random effect. 

dv_gender = dv_c %>%
  filter(Type == "Gender")
dv_gender$Concept = as.factor(dv_gender$Concept)
#The maximal random-effect model couldn't be identified because the random effects outnumber the observations
lm_gender = lmer(value~Statement*Concept+(1+Concept*Statement|index), dv_gender)

#we therefore fitted by-subject random slopes separately for Concept and Statement. 
lm_gender = lmer(value~Statement*Concept+(1+Concept+Statement|index), dv_gender)
anova(lm_gender)
summary(lm_gender)

#Planned contrasts [the results automatically gave all possible contrasts but we only focus on the ones of interest -- see the paper for details]
difflsmeans(lm_gender)
```


```{r message=FALSE, warning=FALSE, echo=FALSE}
gender_graph <- dv_gender %>%
  group_by(Concept, Statement) %>%
  summarise(Mean = mean(value,na.rm=T),
            sd = sd(value),
            upper = Mean + ci.high(value),
            lower = Mean - ci.low(value))

ggplot(gender_graoh,aes(x=Concept, y=Mean, fill=Statement, label = round(Mean, digits=2))) +
  geom_bar(position="dodge", stat="identity", col = "black") + scale_fill_manual(values=c("grey", "white")) +
  geom_errorbar(   aes( ymax=upper, ymin=lower ) , 
                     		width   =.25,
	                    	linetype="solid", position=position_dodge(.9)
	                    	) + 
  theme_bw() + ggtitle("Ratings of Statements by Concept and Statement Type") + geom_text(size = 3, position = position_dodge(width=.9), vjust=7)
```


##The model testing the effects of statement type and concept type and their interaction 
```{r message=FALSE, warning=FALSE}
dv_all = within(dv_tidy, {Type = ifelse(Concept %in% c("Art", "Criminal", "Love", "Friend", "Mentor", "Comedian", "Minister", "Theory", "Boyfriend", "Argument"), "DualCharacter", ifelse(Concept %in% c("Rustling", "Welder", "Catalog", "Chair", "Firefighter", "Uncle", "Cashier", "Stroller", "Obituary", "Cousin"), "Control", ifelse(Concept=="Man", "Man",  ifelse(Concept=="Woman", "Woman", "NaturalKind"))))})


#To simplify the comparisons and keep the comparisons consistent across all experiments, we chose not to include natural kind in the paper because they are not of our interest and our gender vignettes did not pit DNA against appearance (like the natural kinds vignettes in Knobe et al.) but rather concerned individuals with an unambiguous gender identity [cisgender individuals who are not transgender] but transgressed abstract socio-cultural gender norms (see the full paper for details). 

dv_full = dv_all %>%
  filter(Type == "Man"| Type == "Woman" | Type == "DualCharacter" | Type == "Control") %>%
  mutate(Concept = as.factor(Concept),
         Type = as.factor(Type))

#Interaction
lm_full = lmer(value~Type*Statement+(1+Statement|Concept)+(1+Type*Statement|index), dv_full)
anova(lm_full)
summary(lm_full)

difflsmeans(lm_full)

#change reference level
lm_relevel = lmer(value~relevel(Type, ref="DualCharacter")*Statement+(1+Statement|Concept)+(1+Type*Statement|index), dv_full)
summary(lm_relevel)

```

##Graph
```{r message=FALSE, warning=FALSE, echo=FALSE}
library(plyr)
dv_full$Statement = mapvalues(dv_full$Statement, from = c("Member", "Nonmember"), to = c("is a member in a sense", "ultimately not truly a member"))
detach(package:plyr)

graph_full <- dv_full %>%
  group_by(Type, Statement) %>%
  summarise(Mean = mean(value,na.rm=T),
            sd = sd(value),
            upper = Mean + ci.high(value),
            lower = Mean - ci.low(value))

ggplot(graph_full,aes(x=Type, y=Mean, fill=Statement, label = round(Mean, digits=2))) +
  geom_bar(position="dodge", stat="identity", col="snow4") + scale_fill_manual(values=alpha(c("gray85", "skyblue2"), .8)) +
  geom_errorbar(   aes( ymax=upper, ymin=lower ) , 
                     		width   =.25,
	                    	linetype="solid", col = "gray19", position=position_dodge(.9)
	                    	) + 
  theme_bw() + ggtitle(label = "Ratings of Endorsement for", subtitle = "'is a member in a sense' vs. 'ultimately not truly a member' in Exp. 3") + geom_text(size = 3, position = position_dodge(width=.9), col = "black", vjust=5) + scale_x_discrete(limits = c("DualCharacter", "Control", "Man", "Woman")) + scale_y_discrete(limits=seq(1,7, by=1))+labs(x = "Concept Type", y = "Participants' Endorsement of Statement") + coord_cartesian(ylim=c(1,7)) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5, size = 12))
```

##BayesFactor analyses for examining to which type of concepts Man and Woman are closest to, respectively.

```{r}
#creating new Type variables to prepare for the BayesFactor analyses.
##Tyoe is for the original model A where every vfactor is kept separate
##Type1 is for the model B where Dual-Character and Man are treated as the same
##Type2 is for the model C where Control and Man are treated as the same
##Type3 is for the model D where Dual-Character and Woman are treated as the same
##Type4 is for the model E where Control and Woman are treated as the same

dv_bayes = dv_full %>%
  mutate(Type1 = recode(Type, "c('DualCharacter', 'Man') = 'DM'"), Type2 = recode(Type, "c('Control', 'Man') = 'CM'"), Type3 = recode(Type, "c('DualCharacter', 'Woman') = 'DW'"), Type4 = recode(Type, "c('Control', 'Woman') = 'CW'"), Type5 = recode(Type, "c('Control', 'DualCharacter') = 'CD'"))

dv_bayes$value = as.numeric(dv_bayes$value)

#bfA is the all-different model where Dual-Character, Control, Man, and Woman are all separate
bfA = lmBF(value~Type+Statement+Type*Statement, data = as.data.frame(dv_bayes), whichRandom = c("Concept", "index"))
bfa

#bfB is the model A where man = dual character but not others

bfB = lmBF(value~Type1+Statement+Type1*Statement, data = as.data.frame(dv_bayes), whichRandom = c("Concept", "index"))
bfB

#compare model B and the all-different model A
bf_testsAB = c(bfA, bfB)
bf_testsAB

#since bfA's Bayes factor is bigger than that of bfB, we put bfA's factor as the numerator and bfB's factor as the denominator to see how much bigger bfA factor is than bfB factor.
bf_testsAB[1]/bf_testsAB[2]

#bfC is the model C where man = control but not others
bfC = lmBF(value~Type2+Statement+Type2*Statement, data = as.data.frame(dv_bayes), whichRandom = c("Concept", "index"))
bfC

#compare model C and the all-different model A
bf_testsAC = c(bfA, bfC)
bf_testsAC

#since bfA's Bayes factor is bigger than that of bfC, we put bfA's factor as the numerator and bfC's factor as the denominator to see how much bigger bfA factor is than bfC's factor.
bf_testsAC[1]/bf_testsAC[2] 

#now we directly compare Model B and C
bf_testsBC = c(bfB, bfC)
bf_testsBC

#since bfC's Bayes factor is bigger than that of bfB, we put bfC's factor as the numerator and bfB's factor as the denominator to see how much bigger bfC's factor is than bfB's factor.
bf_testsBC[2]/bf_testsBC[1]

#bf4 is the model D where woman = dual but not others
bfD = lmBF(value~Type3+Statement+Type3*Statement, data = as.data.frame(dv_bayes), whichRandom = c("Concept", "index"))
bfD

#compare model D and all-different model A
bf_testsAD = c(bfA, bfD)
bf_testsAD
bf_testsAD[1]/bf_testsAD[2]

#bfE is the model E where woman = control but not others
bfE = lmBF(value~Type4+Statement+Type4*Statement, data = as.data.frame(dv_bayes), whichRandom = c("Concept", "index"))
bfE

#compare model E and the all-different model A
bf_testsAE = c(bfA, bfE)
bf_testsAE
bf_testsAE[1]/bf_testsAE[2]

#bfF is the model E where control = dual-character but not others
bfF = lmBF(value~Type5+Statement+Type5*Statement, data = as.data.frame(dv_bayes), whichRandom = c("Concept", "index"))
bfF
```
Bayes factors might change slightly each time the analyses are re-ran due to the nature of the stochastic approximation approach to calculating Bayes factors. 


#Study 3b [Society Version -- details not reported in the paper]

```{r message=FALSE, warning=FALSE, include=FALSE}
dm = read.csv("~/Desktop/Stanford/Dual Character Concepts/Dual Character Concept Data/Study 3b.csv")

#Remove participants who did not answer the attention check question correctly.
dm = dm %>%
  filter(Filter==1)

#Turn dataset into long form. 
dm_tidy = dm %>%
  mutate(index=rownames(dm)) %>%
  gather(variable, value, Clear.Art:Ultim.Minister) %>%
  group_by(index) %>%
  separate(variable, into=c("Statement", "Concept"))

dm_tidy$value = as.numeric(dm_tidy$value)

#Label variables
dm_tidy$Statement = as.factor(dm_tidy$Statement)
levels(dm_tidy$Statement)[levels(dm_tidy$Statement)=="Clear"] <- "Member"
levels(dm_tidy$Statement)[levels(dm_tidy$Statement)=="Ultim"] <- "Nonmember"

dm_c = within(dm_tidy, {Type = ifelse(Concept %in% c("Art", "Criminal", "Love", "Friend", "Mentor", "Comedian", "Minister", "Theory", "Boyfriend", "Argument"), "DualCharacter", ifelse(Concept %in% c("Rustling", "Welder", "Catalog", "Chair", "Firefighter", "Uncle", "Cashier", "Stroller", "Obituary", "Cousin"), "Control", ifelse(Concept %in% c("Man", "Woman"), "Gender", "NaturalKind")))})
```

##Demographics
```{r message=FALSE, warning=FALSE}
#1 = Female, 2 = Male, 3 = Other
prop.table(table(dm$Gender))
#Age
summary(dm$Age)
#Turns out one participant did not provide their age but instead put irrelevant words -- we did the following procedure to eliminate this to calculate average age and the age range:
dm$Age = as.numeric(as.character(dm$Age))
summary(dm$Age)
```

##Compare Man and Woman to decide whether to combine or separate them in subsequent analyses.
```{r message=FALSE, warning=FALSE}
#since there's only 1 concept within Man and Woman respectively, we do not include Concept but only subject (index) as a random effect. 

dm_gender = dm_c %>%
  filter(Type == "Gender")
lmm_gender = lmer(value~Statement*Concept+(1+Concept*Statement|index), dm_gender) #as before, we fitted a maximal random-effects structure

#the maximal model didn't converge and said that the number of observations was smaller than the number of random effects - we therefore removed the by-subject random slope for the Concept*Statement interaction since each participant only saw two concepts (man and woman). 

lmm_gender = lmer(value~Statement*Concept+(1+Concept+Statement|index), dm_gender)
anova(lmm_gender)
summary(lmm_gender)

difflsmeans(lmm_gender)
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
gender_graph_m <- dm_gender %>%
  group_by(Concept, Statement) %>%
  summarise(Mean = mean(value,na.rm=T),
            sd = sd(value),
            upper = Mean + ci.high(value),
            lower = Mean - ci.low(value))

ggplot(gender_graph_m,aes(x=Concept, y=Mean, fill=Statement, label = round(Mean, digits=2))) +
  geom_bar(position="dodge", stat="identity", col = "black") + scale_fill_manual(values=c("grey", "white")) +
  geom_errorbar(   aes( ymax=upper, ymin=lower ) , 
                     		width   =.25,
	                    	linetype="solid", position=position_dodge(.9)
	                    	) + 
  theme_bw() + ggtitle("Ratings of Statements by Concept and Statement Type") + geom_text(size = 3, position = position_dodge(width=.9), vjust=7)
```

##The model testing the effects of statement type and concept type and their interaction 
```{r message=FALSE, warning=FALSE}
dm_all = within(dm_tidy, {Type = ifelse(Concept %in% c("Art", "Criminal", "Love", "Friend", "Mentor", "Comedian", "Minister", "Theory", "Boyfriend", "Argument"), "DualCharacter", ifelse(Concept %in% c("Rustling", "Welder", "Catalog", "Chair", "Firefighter", "Uncle", "Cashier", "Stroller", "Obituary", "Cousin"), "Control", ifelse(Concept=="Man", "Man",  ifelse(Concept=="Woman", "Woman", "NaturalKind"))))})

dm_full = dm_all %>%
  filter(Type == "Man"| Type == "Woman" | Type == "DualCharacter" | Type == "Control") %>%
  mutate(Concept = as.factor(Concept),
         Type = as.factor(Type))

#Interaction
#Unlike in the examination of the differences between Man and Woman, where there's only one item in each kind, here we treat Concept (specific items) as a random effect because in each of Control and Dual-Character, there are 10 items and every participant would rate all the items. We fitted a maximal random-effects model.

lmm_full = lmer(value~Type*Statement+(1+Statement|Concept)+(1+Type*Statement|index), dm_full)
anova(lmm_full)
summary(lmm_full)

difflsmeans(lmm_full)
```

##Graph
```{r}
full_graph_m <- dm_full %>%
  group_by(Type, Statement) %>%
  summarise(Mean = mean(value,na.rm=T),
            sd = sd(value),
            upper = Mean + ci.high(value),
            lower = Mean - ci.low(value))

ggplot(full_graph_m,aes(x=Type, y=Mean, fill=Statement, label = round(Mean, digits=2))) +
  geom_bar(position="dodge", stat="identity", col="black") + scale_fill_manual(values=c("grey", "white")) +
  geom_errorbar(   aes( ymax=upper, ymin=lower ) , 
                     		width   =.25,
	                    	linetype="solid", position=position_dodge(.9)
	                    	) + 
  theme_bw() + ggtitle("Ratings of Statements by Concept and Statement Type") + geom_text(size = 3, position = position_dodge(width=.9), vjust=7) + scale_x_discrete(limits = c("DualCharacter", "Control", "Man", "Woman")) + scale_y_discrete(limits=seq(0,7, by=1))+labs(x = "Concept Type")
```

##Bayes Factor Analyses
```{r}
#creating new Type variables to prepare for the BayesFactor analyses.
##Tyoe is for the original model A where every vfactor is kept separate
##Type1 is for the model B where Dual-Character and Man are treated as the same
##Type2 is for the model C where Control and Man are treated as the same
##Type3 is for the model D where Dual-Character and Woman are treated as the same
##Type4 is for the model E where Control and Woman are treated as the same

dm_bayes = dm_full %>%
  mutate(Type1 = recode(Type, "c('DualCharacter', 'Man') = 'DM'"), Type2 = recode(Type, "c('Control', 'Man') = 'CM'"), Type3 = recode(Type, "c('DualCharacter', 'Woman') = 'DW'"), Type4 = recode(Type, "c('Control', 'Woman') = 'CW'"))

dm_bayes$value = as.numeric(dm_bayes$value)

#bm1 is the all-different model A where Dual-Character, Control, Man, and Woman are all separate
bmA = lmBF(value~Type+Statement+Type*Statement, data = as.data.frame(dm_bayes), whichRandom = c("Concept", "index"))
bm1

#bmB is the model B where man = dual character but not others

bmB = lmBF(value~Type1+Statement+Type1*Statement, data = as.data.frame(dm_bayes), whichRandom = c("Concept", "index"))
bmB

#compare model A and the all-different model
bm_testsAB = c(bmA, bmB)
bm_testsAB

#since bmA's Bayes factor is bigger than that of bmB, we put bmA's factor as the numerator and bmB's factor as the denominator to see how much bigger bm1 factor is than bm2 factor.
bm_testsAB[1]/bm_testsAB[2]

#bm3 is the model C where man = control but not others
bmC = lmBF(value~Type2+Statement+Type2*Statement, data = as.data.frame(dm_bayes), whichRandom = c("Concept", "index"))
bmC

#compare model C and the all-different model A
bm_testsAC = c(bmA, bmC)
bm_testsAC

#since bmA's Bayes factor is bigger than that of bmC, we put bmA's factor as the numerator and bmC's factor as the denominator to see how much bigger bm1 factor is than bmC's factor.
bm_testsAC[1]/bm_testsAC[2] 

#now we directly compare Model B and C
bm_testsBC = c(bmB, bmC)
bm_testsBC

#since bmC's Bayes factor is bigger than that of bmB, we put bmC's factor as the numerator and bmB's factor as the denominator to see how much bigger bmC's factor is than bmB's factor.
bm_testsBC[2]/bm_testsBC[1]

#bmD is the model D where woman = dual but not others
bmD = lmBF(value~Type3+Statement+Type3*Statement, data = as.data.frame(dm_bayes), whichRandom = c("Concept", "index"))
bmD

#compare model D and all-different model A
bm_testsAD = c(bmA, bmD)
bm_testsAD
bm_testsAD[1]/bm_testsAD[2]

#bmE is the model E where woman = control but not others
bm6 = lmBF(value~Type4+Statement+Type4*Statement, data = as.data.frame(dm_bayes), whichRandom = c("Concept", "index"))
bm6

#compare model E and the all-different model A
bm_testsAE = c(bmA, bmE)
bm_testsAE
bm_testsAE[1]/bm_testsAE[2]

#compare models D and E
bm_testsDE = c(bmD, bmE)
bm_testsDE
bm_testsDE[2]/bm_testsDE[1]
```
