---
title: "Study 5"
output: html_notebook
---

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(lmerTest)
library(car)
library(lme4)
library(knitr)
library(BayesFactor)
library(gridExtra)
library(cowplot)
```

#clean up data and calculating demographics and basic descriptive data
```{r}
#load data
dr = read.csv("~/Desktop/Stanford/Dual Character Concepts/Dual Character Concept Data/Study 5.csv")

#filter out those who provided nonsensical responses
dr_tidy = dr %>%
  mutate(subject = row.names(dr)) %>%
  filter(Nonsense !=1 | is.na(Nonsense)) 

#get the number of participants that remain
num_1 = length(dr_tidy$subject)

#get participant mean age
mean_age = mean(dr_tidy$Age)
mean_age
summary(dr_tidy$Age)
#get participant gender information (1 == female, 2 == male)
dr_tidy$Gender = as.factor(dr_tidy$Gender)
sum_gender = summary(dr_tidy$Gender)
sum_gender
prop.table(sum_gender)

#get the number of "man" responses that remain
num_man1 = dr_tidy %>%
  filter(Man >=1) 
num_mantot = length(num_man1$subject)
num_mantot

#get the numner of "woman" responses that remain

num_woman1 = dr_tidy %>%
  filter(Woman >=1) 
num_womantot = length(num_woman1$subject)
num_womantot

#calculate the mean scores for "man" and "woman" and where they fall against the mid-point of the scale
t.test(dr$Man, mu=4)
t.test(dr$Woman, mu=4)

#filter out those who did not significantly endorse the naturalness of the statements
dr_sig = dr_tidy %>%
  filter(Man >=4 | is.na(Man)) %>%
   filter(Woman >=4 | is.na(Woman))

#get the number of participants who gave a 4 or above for the statements
num_2 = length(dr_sig$subject)

#calculate the proportion of participants who gave a >=4
prop.above4 = num_2/num_1
prop.above4

#calculate the number of "man" responses that remain
dr_man =  dr_tidy %>%
  filter(Man >=4)
num_man = length(dr_man$subject)
num_man

#calculate the proportion of "man" responses that are 4 or above
prop.man4 = num_man/num_mantot
prop.man4

#calculate the number of "woman" responses that remain
dr_woman =  dr_tidy %>%
  filter(Woman >=4)
num_woman = length(dr_woman$subject)
num_woman

#calculate the proportion of "woman" responses that are 4 or above
prop.woman4 = num_woman/num_womantot
prop.woman4
```

After we filtered out those who did not give comprehensible answers, we have a total of 385 participants (48% female, mean age: 35.58). Of those 385 participants, 195 answered the questions about "man" and 190 about "woman".

Among the 195 participants who responded to "man", 170 (87%) rated the naturalness of the "true man" statement with a 4 or above on a 7-point scale. Among the 190 participants who responded to "woman", 151 (79%) rated the naturalness of the "true woman" statement with a 4 or above on a 7-point scale. 

#For "man"
```{r}
#number of participants who had "moral" for "man"
dr_manmoral = dr_sig %>%
  filter(Man >= 1 & Moral == 1)
num_mmoral = length(dr_manmoral$subject)
prop.manmoral = num_mmoral/num_man
prop.manmoral

#number of participants who had stereotypical values for "man"
dr_manstereo = dr_sig %>%
  filter(Man >= 1 & Stereotypical == 1)
num_mstereo = length(dr_manstereo$subject)
prop.mstereo = num_mstereo/num_man
prop.mstereo

#number of participants who had vague values for "man"
dr_manvague = dr_sig %>%
  filter(Man >= 1 & Vague.Value == 1)
num_mvague = length(dr_manvague$subject)
prop.mvague = num_mvague/num_man
prop.mvague

#number of participants who had identity for "man"
dr_manid = dr_sig %>%
  filter(Man >= 1 & Identity == 1)
num_mid = length(dr_manid$subject)
prop.mid = num_mid/num_man
prop.mid

#number of participants who had other for "man"
dr_manot = dr_sig %>%
  filter(Man >= 1 & Other == 1)
num_mot = length(dr_manot$subject)
prop.mot = num_mot/num_man
prop.mot
```

#For "woman"
```{r}
#number of participants who had "moral" for "woman"
dr_wmanmoral = dr_sig %>%
  filter(Woman >= 1 & Moral == 1)
num_wmmoral = length(dr_wmanmoral$subject)
prop.wmanmoral = num_wmmoral/num_woman
prop.wmanmoral

#number of participants who had stereotypical values for "woman"
dr_wmanstereo = dr_sig %>%
  filter(Woman >= 1 & Stereotypical == 1)
num_wmstereo = length(dr_wmanstereo$subject)
prop.wmstereo = num_wmstereo/num_woman
prop.wmstereo

#number of participants who had vague values for "woman"
dr_wmanvague = dr_sig %>%
  filter(Woman >= 1 & Vague.Value == 1)
num_wmvague = length(dr_wmanvague$subject)
prop.wmvague = num_wmvague/num_woman
prop.wmvague

#number of participants who had identity for "woman"
dr_wmanid = dr_sig %>%
  filter(Woman >= 1 & Identity == 1)
num_wmid = length(dr_wmanid$subject)
prop.wmid = num_wmid/num_woman
prop.wmid

#number of participants who had other for "woman"
dr_wmanot = dr_sig %>%
  filter(Woman >= 1 & Other == 1)
num_wmot = length(dr_wmanot$subject)
prop.wmot = num_wmot/num_woman
prop.wmot
```

#making plots for the proportions comparing "man" and "woman"
```{r}
woman_p = c(prop.wmanmoral, prop.wmstereo, prop.wmvague, prop.wmid, prop.wmot)
man_p = c(prop.manmoral, prop.mstereo, prop.mvague, prop.mid, prop.mot)
graph_w = data.frame(woman_p, man_p)
graph_w_tidy = graph_w %>%
  mutate(item=c("Moral", "Stereotypical", "Vague", "Identity", "Other")) %>%
  gather(variable, value, woman_p, man_p) %>%
  group_by(item) %>%
  separate(variable, into = "Target")

ggplot(graph_w_tidy, aes(x=item, y=value, fill=Target,  label = round(value, digits=2))) + geom_bar(position="dodge", stat="identity", color="gray40") + scale_fill_manual(values=c("skyblue2", "pink"), labels = c("Man", "Woman")) + scale_x_discrete(limits = c("Moral", "Stereotypical", "Vague", "Identity", "Other")) +
  theme_bw() + ggtitle("Proportion of Response Type") + geom_text(size = 3, position = position_dodge(width=.9), vjust=5) 
```

#Compare the proportions of responses falling in each coding category for "man" and "woman" using chisq.test
```{r}
x = c(num_mmoral, num_mstereo, num_mvague, num_mid, num_mot) # "man"
y = c(num_wmmoral, num_wmstereo, num_wmvague, num_wmid, num_wmot) #"woman"
chisq.test(data.frame(x,y))
```